Latent Variable Clustering for Classification of Events in the AT-TPC

### 2020-06-02 doc/Manuscript/article.tex
Updates from Overleaf

\section{Results and Discussions}\label{sec:results}
The principal challenge in the AT-TPC experiments that we are trying to solve is the reliance on labelled samples in the analysis as future experiments may not have as visually dissimilar reaction products  as we observe in the ${}^{46}$Ar experiment.  The  ${}^{46}$Ar experiment does, however, provide a useful example where we can then explore unsupervised techniques. In this chapter, we explore the application of clustering techniques to events represented in latent spaces.

>>>>

\section{Results and Discussions}\label{sec:results}
\begin{itemize}
\item Clear out the "methods" like parts.
\item merge 5.1 and 5.2 - keeping point 1 in mind.
\item merge 5.3 5.4 and 5.6 and create table from figure 10, 11 and 12. 
\item go over 5.7 - mention instability in MIXAE results, peak performance of MIXAE is good - consistency is not. 
\item remove fig. 14 and fig 15. 
\end{itemize}

The principal challenge in the AT-TPC experiments that we are trying to solve is the reliance on labelled samples in the analysis as future experiments may not have as visually dissimilar reaction products  as we observe in the ${}^{46}$Ar experiment.  The  ${}^{46}$Ar experiment does, however, provide a useful example where we can then explore unsupervised techniques. In this chapter, we explore the application of clustering techniques to events represented in latent spaces.
